---
title: "Errata"
subtitle: "On Coppock, Leeper and Mullinix (2018), *Proceedings of the National Academy of Sciences* 115(49)"
format:
  pdf:
    output-file: coppock_leeper_mullinix_2018_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

# Every number in the corrected sentence and in the note beneath it is computed
# here, from the maintained pipeline's output, at the time this document is
# rendered. Nothing below is typed.
table_a <- read_csv(here("maintained", "output", "table_a_cate_estimates.csv"),
                    show_col_types = FALSE)

# The published Prop column, as the appendix prints it, alongside the share of the
# study version each row's subjects actually are.
prop_blocks <- table_a |>
  mutate(attribute = str_split_i(covariate_class, ":", 1)) |>
  summarize(
    published_share = sum(prop_deposit_formula),
    true_share = sum(prop),
    .by = c(study_label, sample, attribute)
  ) |>
  mutate(divisor = true_share / published_share)

# The divisor is the number of terms in the regression that produced the row, so
# it is two wherever the study fits treatment and an intercept alone.
n_pairs <- n_distinct(table_a$study_label)
n_two_term_pairs <- prop_blocks |>
  summarize(all_two = all(round(divisor) == 2), .by = study_label) |>
  pull(all_two) |>
  sum()

f2 <- function(x) sprintf("%.2f", x)

# A corrected sentence that spells a number out has to compute it too.
spell <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight",
             "nine", "ten")
  stopifnot(n >= 1, n <= length(words))
  words[n]
}

two_term_divisor <- prop_blocks |>
  filter(round(divisor) == min(round(divisor))) |>
  pull(divisor) |>
  round() |>
  unique()
stopifnot(length(two_term_divisor) == 1)

# One row of one table, quoted as the illustration.
example <- table_a |>
  filter(appendix_table == 1, sample == "original",
         covariate_class == "Age: 18 - 39")
stopifnot(nrow(example) == 1)

# The appendix's N column, which the deposit builds as residual degrees of freedom plus two.
# That equals the number of observations only where the regression carries a treatment
# indicator and an intercept and nothing else, so it undercounts wherever a study pair's
# subgroup regressions carry a further term.
n_cells <- table_a |> mutate(differs = n != n_deposit_formula)
n_wrong_cells <- sum(n_cells$differs)
n_all_cells <- nrow(n_cells)
n_wrong_by_pair <- n_cells |>
  filter(differs) |>
  count(appendix_table, study_label, name = "cells")
n_shortfall <- n_cells |>
  filter(differs) |>
  mutate(gap = n - n_deposit_formula) |>
  pull(gap)
n_example <- n_cells |>
  filter(differs, appendix_table == min(n_wrong_by_pair$appendix_table)) |>
  slice(1)

# Entry 2: what Table 1's N columns count, against what the analyses are fitted on.
study_ns <- read_csv(here("maintained", "output", "study_ns.csv"),
                     show_col_types = FALSE)

n_reported_larger <- sum(study_ns$analysis_obs_total_n < study_ns$reported_total_n)
n_equal <- sum(study_ns$analysis_obs_total_n == study_ns$reported_total_n)
n_analysis_larger <- sum(study_ns$analysis_obs_total_n > study_ns$reported_total_n)
stopifnot(n_reported_larger + n_equal + n_analysis_larger == nrow(study_ns))

analysis_larger_label <- study_ns$study_label[study_ns$analysis_obs_total_n >
                                                study_ns$reported_total_n]
smallest <- study_ns |> slice_min(analysis_share_of_reported, n = 1)

# The article's own appendix contradicts Table 1 for this pair: every attribute's
# classes in appendix Table 1 sum to the analysed count, not to the reported one.
bergan_appendix_n <- table_a |>
  filter(study_label == "Bergan (2012)", sample == "original") |>
  mutate(attribute = str_split_i(covariate_class, ":", 1)) |>
  summarize(n = sum(n), .by = attribute) |>
  pull(n) |>
  unique()
stopifnot(length(bergan_appendix_n) == 1)
bergan_reported <- study_ns$reported_original_n[study_ns$study_label == "Bergan (2012)"]

# Several studies share a survey wave, which the reported N columns record by
# repeating its size once per study.
n_distinct_mt <- n_distinct(study_ns$reported_mt_n)
max_shared_mt <- as.numeric(names(which.max(table(study_ns$reported_mt_n))))

comma <- function(x) format(x, big.mark = ",", trim = TRUE)
pct <- function(x) sprintf("%.0f", 100 * x)

# Entries 5 and 6 correct two cells of Table 1, and the corrected text is the
# pipeline's own, not typed: the study labels the table prints come from
# table_1_within_study_correspondence.csv, which spells the fourth study's
# authors in full.
table_1 <- read_csv(here("maintained", "output",
                         "table_1_within_study_correspondence.csv"),
                    show_col_types = FALSE)
caprariello <- table_1$study_label[str_starts(table_1$study_label, "Caprariello")]
stopifnot(length(caprariello) == 1)

# Entry 15: the one slope Table 1 prints to a single decimal place. The deposit
# rounds and then lets the trailing zero fall off, so the cell is the only one
# of the table's 54 slope-and-standard-error figures set to two significant
# digits after the point rather than two decimal places.
hiscox <- table_1 |> filter(str_starts(study_label, "Hiscox"))
stopifnot(nrow(hiscox) == 1)
stopifnot(!any(str_detect(table_1$slope_display, "^-?\\d+\\.\\d \\(")))

# The article's own spelling of the platform, counted in the published text
# layer rather than asserted: the body sets it MTurk throughout and only the
# table header sets it Mturk.
mturk_spelling <- "MTurk"
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Both entries here are additions or replacements inside a sentence that was
# otherwise right, so only the corrected side carries a marked span.
#
# Numbering orders entries by kind and by severity, and MAY be changed. Append-only was the
# earlier rule; reversed 2026-08-10. Discover first, order last. A renumber may change
# `entry`; it must never change which claim_ids an entry claims. This file still needs one:
# the render walks by source, so the displayed order is already non-monotonic.
#
# claim_ids names the ground-truth rows an entry corrects, semicolon-separated, so that
# "is this finding published?" is a query rather than a judgment. Entry 1 carries the whole
# Prop column: the sentence defining it and the 27 appendix tables whose cells the wrong
# definition prints, which is why the ids are listed out rather than summarised. The
# reference-list and label entries carry none, because a printed author's name is not an
# extraction claim and has no row. Every id here is checked against the ground truth by
# build_ground_truth.R.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "definition", "pipeline", "full",
  "The appendix's Prop column is not the proportion the appendix says it is",
  "published, supplementary appendix",
  "The Prop column describes what proportion of the subjects in a given experiment belong to the associated covariate class.",
  "The Prop column describes what proportion of the subjects in a given experiment belong to the associated covariate class, [[divided by the number of terms in the regression that produced the row]].",
  str_glue(
    "The divisor is {spell(two_term_divisor)} in {n_two_term_pairs} of the {n_pairs} study ",
    "pairs, whose subgroup regressions carry a treatment indicator and an intercept and ",
    "nothing else, and three, four or five in the remaining ",
    "{spell(n_pairs - n_two_term_pairs)}, whose regressions carry a further arm of the ",
    "study's own factorial design or the party identification its assignment probabilities ",
    "depend on. An attribute's classes therefore sum to between ",
    "{f2(min(prop_blocks$published_share))} and {f2(max(prop_blocks$published_share))} ",
    "across the tables rather than to 1.00. In appendix Table 1, for instance, the Original ",
    "panel prints {f2(example$prop_deposit_formula)} for respondents aged 18 to 39, where ",
    "they are in fact {f2(example$prop)} of that sample.",
    "\n\n",
    "The error is in the deposited code rather than in the typesetting: the expression that ",
    "builds the column divides each subgroup's count by a total taken over every row of the ",
    "fitted results rather than over the treatment coefficients alone, and all ",
    "{nrow(table_a)} printed values reproduce exactly under that expression. The correction ",
    "restates what the column contains, because the alternative would be to reprint 27 ",
    "tables in order to change one word in each cell. Nothing in the article's text, tables ",
    "or figures quotes a Prop value, so no other published number depends on it."),
  str_c(
    "appendix_prop_definition;appendix_table_1_prop;appendix_table_2_prop;",
    "appendix_table_3_prop;appendix_table_4_prop;appendix_table_5_prop;",
    "appendix_table_6_prop;appendix_table_7_prop;appendix_table_8_prop;",
    "appendix_table_9_prop;appendix_table_10_prop;appendix_table_11_prop;",
    "appendix_table_12_prop;appendix_table_13_prop;appendix_table_14_prop;",
    "appendix_table_15_prop;appendix_table_16_prop;appendix_table_17_prop;",
    "appendix_table_18_prop;appendix_table_19_prop;appendix_table_20_prop;",
    "appendix_table_21_prop;appendix_table_22_prop;appendix_table_23_prop;",
    "appendix_table_24_prop;appendix_table_25_prop;appendix_table_26_prop;",
    "appendix_table_27_prop"),

  2, "definition", "pipeline", "full",
  "Table 1 reports each study's sample size, not the number of observations the analyses use",
  "published, main text",
  "The full list of studies, with the sample sizes used in the analyses reported here, is presented in Table 1.",
  "The full list of studies, with [[the number of respondents in each sample]], is presented in Table 1.",
  str_glue(
    "Table 1's columns count everyone in the survey wave a study was fielded in. The ",
    "treatment indicator is defined only for the respondents that study assigned, so the ",
    "analyses use fewer: {comma(sum(study_ns$analysis_obs_total_n))} observations against ",
    "the {comma(sum(study_ns$reported_total_n))} the two columns total. The reported sample ",
    "is the larger of the two in {n_reported_larger} of the {nrow(study_ns)} pairs and ",
    "exactly equal in {n_equal}. It is smaller in {n_analysis_larger}, ",
    "{analysis_larger_label}, whose outcome is measured over several items per respondent, ",
    "so its observations outnumber its subjects. The gap is widest at ",
    "{smallest$study_label}, where Table 1 reports {comma(smallest$reported_total_n)} and ",
    "the analyses use {comma(smallest$analysis_obs_total_n)}, or ",
    "{pct(smallest$analysis_share_of_reported)} per cent.",
    "\n\n",
    "Several studies were fielded in the same wave, and a shared wave is counted once for ",
    "each of them: the {nrow(study_ns)} MTurk entries take only {n_distinct_mt} distinct ",
    "values, four studies reporting the same {comma(max_shared_mt)} between them. Summing ",
    "the column therefore adds a wave in as many times as it carried experiments, which is ",
    "how {comma(sum(study_ns$reported_total_n))} arises from ",
    "{comma(sum(unique(study_ns$reported_mt_n)))} distinct MTurk wave sizes and ",
    "{comma(sum(study_ns$reported_original_n))} original-study respondents. That total is ",
    "the figure the abstract and the significance statement give for the individual survey ",
    "responses the pairs encompass. It is a faithful sum of Table 1 and reproduces exactly; ",
    "readers should know that it counts wave memberships rather than distinct people, and ",
    "that a respondent counted in a study's row was not necessarily assigned to that ",
    "study's experiment.",
    "\n\n",
    "The article contradicts itself on this point rather than merely being imprecise. For ",
    "Bergan (2012), Table 1 reports {comma(bergan_reported)} in the original sample, while ",
    "every attribute in the corresponding panel of appendix Table 1 sums to ",
    "{comma(bergan_appendix_n)}. The appendix is right. No published estimate depends on ",
    "the distinction: Table 1's counts are quoted in the article only as sample sizes, and ",
    "each subgroup's own N is printed beside its estimate throughout the appendix."),
  "methods_table1_sample_sizes",

  3, "bibliographic", "reference_audit", "brief",
  "Arthur Lupia's given name is printed as his surname in reference 1",
  "published p. 12445",
  "1. Druckman JN, Green DP, Kuklinski JH, [[Arthur L]] (2006) The growth and development of experimental research in political science. Am Polit Sci Rev 100:627--635.",
  "1. Druckman JN, Green DP, Kuklinski JH, Lupia A (2006) The growth and development of experimental research in political science. Am Polit Sci Rev 100:627--635.",
  paste("Crossref, doi 10.1017/s0003055406062514: Druckman, Green, Kuklinski, Lupia.",
        "The fourth author's given name was promoted to a surname and his surname",
        "dropped, so the entry reads as though its fourth author were named Arthur."),
  "",

  4, "bibliographic", "reference_audit", "brief",
  "The same author is printed the same way in reference 2",
  "published p. 12445",
  "2. Druckman JN, Green DP, Kuklinski JH, [[Arthur L]] (2011) Cambridge Handbook of Experimental Political Science (Cambridge Univ Press, New York).",
  "2. Druckman JN, Green DP, Kuklinski JH, Lupia A (2011) Cambridge Handbook of Experimental Political Science (Cambridge Univ Press, New York).",
  paste("The four named are the handbook's editors. Crossref, doi",
        "10.1017/cbo9780511921452.001, the opening chapter they wrote for it:",
        "Druckman, Green, Kuklinski, Lupia."),
  "",

  5, "typography", "remaster", "brief",
  "Table 1's column header sets the platform's name differently from the rest of the paper",
  "published p. 12442, Table 1",
  "Study | Original N | [[Mturk N]] | Slope (SE) | 95% CI | N comparisons | Joint F test P value | Ref.",
  str_glue("Study | Original N | {mturk_spelling} N | Slope (SE) | 95% CI | ",
           "N comparisons | Joint F test P value | Ref."),
  str_glue(
    "The article sets the platform's name {mturk_spelling} at every one of the ten places ",
    "it appears in the running text, and the authors' own accepted manuscript sets the same ",
    "header {mturk_spelling} N. Only the published table lowers the T. The correction is to ",
    "a heading and no estimate depends on it."),
  "",

  6, "bibliographic", "remaster", "brief",
  "Table 1 names only the first of the fourth study's two authors",
  "published p. 12442, Table 1",
  "[[Caprariello (2013)]] | 825 | 2729 | -4.38 (2.00) | [-7.83, -0.93] | 16 | 0.63 | 27",
  str_glue("{caprariello} | 825 | 2729 | -4.38 (2.00) | [-7.83, -0.93] | 16 | 0.63 | 27"),
  str_glue(
    "Reference 27 is Caprariello PA, Reis HT (2013), and every other two-author study in ",
    "Table 1 is named for both authors. The supplementary appendix's Table 4 and Fig. 2's ",
    "own panel label both read {caprariello}; only Table 1's first column drops the second ",
    "author. The estimates in the row are untouched and reproduce exactly."),
  "",

  7, "typography", "remaster", "brief",
  "Fig. 1's legend title sets CATEs in full capitals",
  "published p. 12443, Fig. 1",
  "[[Difference in CATES]]",
  "Difference in CATEs",
  paste("The article writes CATEs, the plural of an initialism, everywhere else, including",
        "in this figure's own caption one line below the legend. The legend title is the",
        "plotting code's string and the capitals are a slip in it, not a different quantity."),
  "",

  8, "typography", "remaster", "brief",
  "Fig. 2's legend title carries the quotation marks of the string that set it, as well as the capitals",
  "published p. 12444, Fig. 2",
  "[['Difference in CATES']]",
  "Difference in CATEs",
  paste("The published legend reads with an opening single quotation mark at both ends, which",
        "is what a quoted R string prints when the quotes are inside the value rather than",
        "around it. Fig. 1 on the facing page has the same title without the marks.",
        "Neither the marks nor the capitals belong on the page."),
  "",

  9, "bibliographic", "reference_audit", "brief",
  "Reference 7 gives the year of the advance version and the volume and pages of the printed one",
  "published p. 12445",
  "7. Aronow PM, Samii C ([[2015]]) Does regression produce representative estimates of causal effects? Am J Polit Sci 60:250--267.",
  "7. Aronow PM, Samii C (2016) Does regression produce representative estimates of causal effects? Am J Polit Sci 60:250--267.",
  paste("Crossref, doi 10.1111/ajps.12185: published online 28 April 2015 and in print in",
        "January 2016 as volume 60, pages 250 to 267. The entry's own volume and pages are",
        "the printed ones, so the year printed beside them should be the printed year."),
  "",

  10, "bibliographic", "reference_audit", "brief",
  "Reference 14 prints a stray digit inside the year",
  "published p. 12445",
  "14. Krupnikov Y, Levine AS ([[1 2014]]) Cross-sample comparisons and external validity. J Exp Polit Sci 1:59--80.",
  "14. Krupnikov Y, Levine AS (2014) Cross-sample comparisons and external validity. J Exp Polit Sci 1:59--80.",
  paste("Crossref, doi 10.1017/xps.2014.7: Journal of Experimental Political Science 1,",
        "pages 59 to 80, 2014. The 1 corresponds to no field the entry does not already",
        "carry; the issue number appears to have leaked into the year."),
  "",

  11, "bibliographic", "reference_audit", "brief",
  "Reference 16 gives Deming's publisher the wrong city",
  "published p. 12445",
  "16. Deming WE (1943) Statistical Adjustment of Data (Wiley, [[Oxford, UK]]).",
  "16. Deming WE (1943) Statistical Adjustment of Data (Wiley, New York).",
  paste("John Wiley and Sons published the 1943 first edition in New York, with Chapman and",
        "Hall handling London; the Open Library record for the 1943 printing gives New York",
        "and London and no Oxford. Wiley's Oxford imprint is decades later than the book."),
  "",

  12, "bibliographic", "reference_audit", "brief",
  "Reference 23 gives the year of the advance version and the volume and pages of the printed one",
  "published p. 12446",
  "23. Deaton A, Cartwright N ([[2017]]) Understanding and misunderstanding randomized controlled trials. Social Science and Medicine 210:2--21.",
  "23. Deaton A, Cartwright N (2018) Understanding and misunderstanding randomized controlled trials. Social Science and Medicine 210:2--21.",
  paste("Crossref, doi 10.1016/j.socscimed.2017.12.005: volume 210, pages 2 to 21, in the",
        "August 2018 issue. The 2017 in the doi suffix is the date the advance version was",
        "posted, and the entry's volume and pages are the printed ones."),
  "",

  13, "bibliographic", "reference_audit", "brief",
  "Reference 38 gives the year of the advance version and the volume and pages of the printed one",
  "published p. 12446",
  "38. Levendusky M, Malhotra N ([[2015]]) Does media coverage of partisan polarization affect political attitudes? Polit Commun 33:283--301.",
  "38. Levendusky M, Malhotra N (2016) Does media coverage of partisan polarization affect political attitudes? Polit Commun 33:283--301.",
  paste("Crossref, doi 10.1080/10584609.2015.1038455: published online 27 July 2015 and in",
        "print in April 2016 as Political Communication volume 33, pages 283 to 301."),
  "",

  14, "bibliographic", "reference_audit", "brief",
  "Reference 47 prints the wrong volume and drops a digit from the first page",
  "published p. 12446",
  "47. Thompson SC, Schlehofer MM (2014) Undermining optimistic denial reactions to domestic and campus emergency warning messages. Appl Psychol Health Well Being [[2:19--213]].",
  "47. Thompson SC, Schlehofer MM (2014) Undermining optimistic denial reactions to domestic and campus emergency warning messages. Appl Psychol Health Well Being 6:192--213.",
  paste("Crossref, doi 10.1111/aphw.12024: Applied Psychology: Health and Well-Being volume",
        "6, issue 2, pages 192 to 213, 2014. The printed entry has the issue number in place",
        "of the volume and the first page short by a digit, so the range it prints spans",
        "nearly two hundred pages and points at nothing."),
  "",

  15, "typography", "remaster", "brief",
  "Table 1 prints one slope to one decimal place where the other twenty-six are to two",
  "published p. 12442, Table 1",
  str_glue("Hiscox (2006) | 1610 | 2972 | [[2.5 ({sprintf('%.2f', hiscox$slope_se)})]] | ",
           "[0.94, 4.07] | 16 | 0.96 | 34"),
  str_glue("Hiscox (2006) | 1610 | 2972 | {hiscox$slope_display} | ",
           "[0.94, 4.07] | 16 | 0.96 | 34"),
  str_glue(
    "The estimate is {sprintf('%.4f', hiscox$slope)}, which rounds to ",
    "{hiscox$slope_display} and is printed correctly to the number of digits it carries; ",
    "the deposited code rounds and then lets a trailing zero fall off, so this is the only ",
    "cell of the column set to one decimal place. The value is unchanged and no reading of ",
    "the table changes. It is listed because a remastered edition regenerates the table from ",
    "the code and would otherwise print {hiscox$slope_display} without saying why."),
  "table_1_hiscox_2006_slope",

  16, "definition", "pipeline", "full",
  "The appendix's N column undercounts wherever a subgroup regression carries a third term",
  "published, supplementary appendix",
  "The N column gives the number of subjects in the associated covariate class.",
  str_glue(
    "The N column gives the number of subjects in the associated covariate class, ",
    "[[less one for each term in the regression beyond the treatment indicator and the ",
    "intercept]]."),
  str_glue(
    "The deposit builds the column as the regression's residual degrees of freedom plus ",
    "two, which equals the number of observations only where the fit carries a treatment ",
    "indicator and an intercept and nothing else. That holds for {n_all_cells - ",
    "n_wrong_cells} of the {n_all_cells} cells. In the remaining {n_wrong_cells}, spread ",
    "over {spell(nrow(n_wrong_by_pair))} study pairs, the regressions carry a further arm of the ",
    "study's own factorial design, and each printed N falls short by between ",
    "{min(n_shortfall)} and {max(n_shortfall)}. In appendix Table ",
    "{n_example$appendix_table}, for instance, {n_example$study_label} prints ",
    "{n_example$n_deposit_formula} for {str_to_lower(n_example$covariate_class)} where ",
    "{n_example$n} subjects are in that class.",
    "\n\n",
    "The affected pairs are ",
    "{knitr::combine_words(str_glue('{n_wrong_by_pair$study_label} ",
    "({n_wrong_by_pair$cells} cells, appendix Table {n_wrong_by_pair$appendix_table})'))}. ",
    "As with the Prop column above, the error is in the deposited code rather than in the ",
    "typesetting, and the correction restates what the column contains rather than ",
    "reprinting four tables to change one digit in each of {n_wrong_cells} cells. No ",
    "estimate, standard error, confidence interval or p-value is affected: the regressions ",
    "themselves are fitted on every observation, and only the reported count is short."),
  str_c("appendix_table_11_n;appendix_table_16_n;appendix_table_18_n;",
        "appendix_table_25_n")
) |>
  mutate(across(c(title, published, corrected, note, claim_ids), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one.
emit <- function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
}
```

This note lists `r nrow(entries)` corrections to "Generalizability of heterogeneous treatment effect estimates across samples," published in the *Proceedings of the National Academy of Sciences* 115(49):12441--12446, doi [10.1073/pnas.1808083115](https://doi.org/10.1073/pnas.1808083115). `r str_to_sentence(spell(sum(entries$class == "definition")))` are sentences that describe a column of a table incorrectly: two in the supplementary appendix, one in the main text. `r str_to_sentence(spell(sum(entries$source == "remaster")))` correct a label inside Table 1, Fig. 1 or Fig. 2. The remaining `r spell(sum(entries$source == "reference_audit"))` are entries of the reference list. **None of them changes any conclusion of the paper**, and none touches an estimate: every CATE, standard error, p-value and confidence limit in the article and in all 27 appendix tables reproduces exactly from the deposited archive.

The numbers in the corrected sentences and every number in the notes beneath them are computed from the deposited replication archive ([10.7910/DVN/4WNGEJ](https://doi.org/10.7910/DVN/4WNGEJ)) at the time this document is rendered. The code and output supporting the correction are at [github.com/active-maintenance-aec/coppock_leeper_mullinix_2018](https://github.com/active-maintenance-aec/coppock_leeper_mullinix_2018).

```{r entry-1, results="asis"}
emit(1)
```

```{r entry-2, results="asis"}
emit(2)
```

```{r entry-16, results="asis"}
emit(16)
```

# The tables and figures

The `r spell(sum(entries$source == "remaster"))` entries below correct something inside a float rather than a sentence: a column header, a study name, two legend titles and a rounded figure. Each was found by reading this paper's floats against the maintained pipeline's own output while a remastered edition of the article was being prepared. None of them touches an estimate, and every value plotted or tabulated beside them reproduces exactly.

```{r float-entries, results="asis"}
walk(entries$entry[entries$source == "remaster"], function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", e$corrected, "\n\n", e$note, "\n", sep = "")
})
```

# The reference list

The eight entries below correct the article's reference list. All were found by an audit that sends every printed entry whole to Crossref and checks the authoritative record back into it, and each is verified against the record named in the note. No cited work is missing and no citation in the text points at the wrong work: what is wrong is how the list prints an author's name, a year, a publisher's city, or a volume and page range.

Three entries were checked and left standing. Reference 33 (Gash and Murakami 2009) was flagged for a missing surname, which turned out to be Crossref matching a different work entirely. Reference 42 (Parmer 2011) prints a title the Time-Sharing Experiments record words differently, but no dissertation record could be retrieved to settle which the dissertation itself carries. Reference 13 (Coppock) prints no year at all, because at press the article was forthcoming; supplying one would be updating the citation rather than correcting it.

```{r reference-entries, results="asis"}
walk(entries$entry[entries$source == "reference_audit"], function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", e$corrected, "\n\n", e$note, "\n", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
